Robust Inferences from Simply Parameterised Models

### 2012-05-16 ms.tex
Added acknowledgement
Added Joey's paper
Random writing

\documentclass[letterpaper, 11pt]{article}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage[left=3cm,top=3cm,right=3cm]{geometry}

@@

\author{%
  Brendon~J.~Brewer$^{1}$\thanks{\tt brewer@physics.ucsb.edu}, 
  Geraint~F.~Lewis$^{2}$,
  Ross Fadely\\
  \medskip\\
  $^1$UCSB\\
  $^2$USyd
}

@@

\section{Background on Bayesian Inference}

@@

\begin{equation}
p(\theta | D) \propto p(\theta) p(D|\theta)|_{D=D_{\rm obs}}
\end{equation}
The various terms in this equation have the following names and meanings.

@@

>>>>

\documentclass[letterpaper, 11pt]{article}
\usepackage{authblk}	% For nice author-affil lists
\usepackage{graphicx}	% For figures
\usepackage{natbib}	% For citet and citep
\usepackage{amsmath}	% for \iint
\usepackage{bbm}	% for blackboard bold numbers
\usepackage[left=3cm,top=3cm,right=3cm]{geometry}

@@

\author[1,2]{Brendon J. Brewer}
\author[3]{Geraint~F.~Lewis}
\author[4]{Ross Fadely}
\affil[1]{\small Dept. of Physics, University of California, Santa Barbara, CA 93106, USA}
\affil[2]{Department of Statistics, University of Auckland, Private Bag 92019, Auckland, New Zealand
}
\affil[3]{Sydney Institute for Astronomy, School of Physics, The University of Sydney, A28, Sydney, 2006, Australia}
\affil[4]{Department of Astronomy, Haverford College, 370 Lancaster Ave., Haverford, PA 19041 USA}

@@

\section{Introduction}

@@

Bayesian Inference is a powerful framework for modelling uncertainty that has
been successfully applied in many scientific fields \citep{}. The basic idea
is that we can model the degree of plausibility of a hypothesis $H$ by a real
number in $[0, 1]$, and that these numbers should be manipulated according to
the rules of probability theory. If we are initially uncertain about some
hypothesis $H$, we model this as a {\it prior probability} $P(H)$. If some other
hypothesis $D$ is discovered to be true, the plausibility of $H$ is updated to
the {\it posterior probability} using Bayes' rule:
\begin{equation}
P(H|D) = \frac{P(H)P(D|H)}{P(D)}
\end{equation}

One common application of Bayesian Inference is for parameter estimation.
Suppose there is some quantity $\theta$ that is unknown. Initially, we describe
our uncertainty by a prior distribution $p(\theta)$. We also know about some
observation or experiment that will yield data $D$ that will provide some
information about $\theta$. We describe our knowledge about this process by 
{\it sampling distributions} $p(D|\theta)$. Then, once a specific data set
$D_{\rm obs}$ has been observed, we update our state of knowledge about $\theta$
to the {\it posterior distribution}:
\begin{equation}
p(\theta | D) \propto p(\theta) p(D|\theta)|_{D=D_{\rm obs}}
\end{equation}
The various terms in this equation have the following names and meanings.

@@

\bibitem[Richards et al.(2011)]{2011arXiv1105.6344R} Richards, J.~W., Lee, 
A.~B., Schafer, C.~M., Freeman, P.~E.\ 2011.\ Prototype selection for 
parameter estimation in complex models.\ ArXiv e-prints arXiv:1105.6344.
